19Q1

### 2019-05-14 19Q1.Rmd
updated Rmd

@@

g2p <- add_column(g2p, Variant_Type = NA, .after = "Alt")

@@

  ifelse(g2p$Ref_Length < g2p$Alt_Length, "INS", NA))))))

@@

g2p$biomarker_type_curated <-
  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "[A-Z0-9]+-[A-Z0-9]+^[>|)]")), "fusion",

@@

@@

  ifelse(!is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "biallelic inactivation")), "biallelic inactivation",
  ifelse(!is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "amplification")), "amplification",
  ifelse(!is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "mutant|mutation")), "mutation",

@@

  ifelse(g2p$biomarker_type == "inframe_deletion", "In_Frame_Del",
  ifelse(g2p$Feature.Names %in% c("EGFR E746_A750del", "EGFR exon 19 deletions", "Exon 19 deletion/insertion", "Exon 19 deletion"), "In_Frame_Ins",

@@

  ifelse(g2p$Feature.Names == "KRAS G12fs*3" | g2p$Feature.Names == "EGFR E746fs*15", "deletion",
  ifelse(!is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "amplification")), "amplification",
  ifelse(g2p$biomarker_type == "microsatellite", "microsatellite",
  ifelse(g2p$biomarker_type == "positive" | !is.na(str_match(string = g2p$Feature.Names, pattern = "positive")), "positive",

@@

  ifelse(!is.na(str_match(string = tolower(g2p$biomarker_type), pattern = "mut")), "mutation", g2p$biomarker_type_curated)))))))))))))))))))))))

g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
g2p$position <- paste0("g.chr", g2p$Chromosome, ":", g2p$End, g2p$Ref, ">", g2p$Alt)
g2p$position <- ifelse(grepl("NA", g2p$position), NA, g2p$position)
g2p <- merge(lineage_converter, g2p, by = "grouped_general_doid", all.y = TRUE)
g2p$Drug_Gene_Lin <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene) | is.na(g2p$group_general_lineage_name), NA, paste0(g2p$Drug, "_", g2p$Gene, "_", g2p$group_general_lineage_name))

@@

g2p_dgls <-  unique (g2p$Drug_Gene_Lin[!is.na(g2p$Drug_Gene_Lin)])
g2p_druggenes <- unique(g2p$Drug_Gene[!is.na(g2p$Drug_Gene)])
g2p_drugs <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[1]))
g2p_genes <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[2]))
g2p_lins <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[3]))
g2p_druggenes
g2p_drugs
g2p_genes
g2p_lins

@@

@@

**RE-FILTER FOR PTMUTS**
```{r merge_filter_drug_data, eval=FALSE}
# Load in Pozdeyev et al. (2016) data
ccle_all <- read.delim("./../htscreens_giant_files/pozdeyev_data/CCLE_drug_response_metrics.csv.gz", sep = ",")
ctrp_all <- read.delim("./../htscreens_giant_files/pozdeyev_data/CTRP_drug_response_metrics.csv.gz", sep = ",")
gdsc_all <- read.delim("./../htscreens_giant_files/pozdeyev_data/GDSC_drug_response_metrics.csv.gz", sep = ",")

@@

# Merge cell line metadata
crispr_melt <- merge(crispr_melt, ccl_meta, by = "Broad_ID", all.x = TRUE)

>>>>

g2p <- unfactorize(g2p)

@@

g2p <- add_column(g2p, Variant_Type = NA, .after = "Alt_Length")

@@

  ifelse(g2p$Ref_Length < g2p$Alt_Length, "INS", "None"))))))

@@

biomarker_type_curated <-

@@

  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "Amplification|amplification")), "amplification",
  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "^PDGFRA [(]")) | !is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "mutant|mutation|mut")), "mutation",

@@

  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "[A-Z0-9|A-Z]+-[A-Z0-9|A-Z]+")) & is.na(str_match(string = g2p$Feature.Names, pattern = "[0-9]+-[0-9]+")), "fusion",

@@

  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "EGFR E746_A750del")), "In_Frame_Del",
  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "EGFR H773>PNPY")), "In_Frame_Ins",

@@

  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "positive")), "positive",
  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "expression")), "expression",

@@

  ifelse(g2p$biomarker_type == "inframe_deletion" | !is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "inframe deletion")), "In_Frame_Del",
  ifelse(!is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "biallelic inactivation")), "biallelic inactivation", NA)))))))))))))))))))))
g2p$biomarker_type_curated <- biomarker_type_curated[,1]
g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
g2p$position <- paste0("g.chr", g2p$Chromosome, ":", g2p$End, g2p$Ref, ">", g2p$Alt)
g2p$position <- ifelse(grepl("NA", g2p$position), NA, g2p$position)
g2p <- merge(lineage_converter, g2p, by = "grouped_general_doid", all.y = TRUE)
g2p$Drug_Gene_Lin <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene) | is.na(g2p$group_general_lineage_name), NA, paste0(g2p$Drug, "_", g2p$Gene, "_", g2p$group_general_lineage_name))

@@

# g2p_dgls <-  unique (g2p$Drug_Gene_Lin[!is.na(g2p$Drug_Gene_Lin)])
# g2p_druggenes <- unique(g2p$Drug_Gene[!is.na(g2p$Drug_Gene)])
# g2p_drugs <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[1]))
# g2p_genes <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[2]))
# g2p_lins <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[3]))
# g2p_druggenes
# g2p_drugs
# g2p_genes
# g2p_lins

@@

DepMap 19Q2 fusion calls:
```{r fusion_calls, eval=FALSE}
fusions <- read.delim("./data_munging/19Q2/CCLE_fusions.csv.gz", header = TRUE, sep = ",")
fusions$LeftGene <- gsub(" .*", "", fusions$LeftGene)
fusions$RightGene <- gsub(" .*", "", fusions$RightGene)
fusions$ <- gsub(" .*", "", fusions$RightGene)
```

@@

```{r merge_filter_drug_data, eval=FALSE}
# Load in Pozdeyev et al. (2016) data
ccle_all <- read.delim("./../htscreens_giant_files/pozdeyev_data/CCLE_drug_response_metrics.csv.gz", sep = ",")
ctrp_all <- read.delim("./../htscreens_giant_files/pozdeyev_data/CTRP_drug_response_metrics.csv.gz", sep = ",")
gdsc_all <- read.delim("./../htscreens_giant_files/pozdeyev_data/GDSC_drug_response_metrics.csv.gz", sep = ",")

@@

# Merge cell line metadata
crispr_melt <- merge(crispr_melt, ccl_meta, by = "Broad_ID", all.x = TRUE)
test_crispr <- unique(select(crispr_melt, Broad_ID, Histology)) %>% count(Histology)
